### 2022-08-25 Bloods Data Sheet.Rmd
Extracted draft plots

```{r}
write.csv(main_df,"C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\Main_Data_Frame (23-08-2022).csv",row.names = FALSE)
```

>>>>

```{r}
write.csv(main_df,"C:\\Users\\thoma\\OneDrive - Murdoch University\\Desktop\\PhD 2022\\Publications\\Study 2 - Bloods\\Main_Data_Frame (25-08-2022).csv",row.names = FALSE)
```

### 2022-08-25 Draft Plots.Rmd
Extracted draft plots

@@

@@

@@

@@

@@

>>>>

```{r}
ggsave(plot=Bla_PLOT_1,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//Blaplot_Draft(25-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)

@@

```{r}
ggsave(plot=LDH_PLOT_1,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//LDHplot_Draft(25-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)

@@

```{r}
ggsave(plot=CK_PLOT_1,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//CKplot_Draft(25-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)

@@

```{r}
ggsave(plot=Na_PLOT_1,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//NAplot_Draft(25-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)

@@

```{r}
ggsave(plot=K_PLOT_1,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//Kplot_Draft(25-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)

@@

```{r}
ggsave(plot=Cl_PLOT_1,"C://Users//thoma//OneDrive - Murdoch University//Desktop//PhD 2022//Publications//Study 2 - Bloods//Plot Drafts//Clplot_Draft(25-08-2022).png", units = "in",width = 12, height = 8, dpi = 1200)
